Software Ticket Quality

### 2017-11-26 proposal/mprop.tex
Work on study design

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background Survey}

% 10 - 12 pages

@@

@@

As the main objective of our research is to determine what makes for a good 
quality ticket, we needed to explore what was previously done in

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background Survey}
% 10 - 12 pages

@@

We analyzed data quality mainly in software organizations and looked at what metrics
are most useful when trying to perform measurements. We also tried to find different
methodologies that either measure data quality or calculate the impact of poor data
quality on the software project.

Secondly, probably the topic of most interest to our research is \emph{issue quality}.
This field is mainly concerned with software tickets and their characteristics: how
important

@@
